Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-20 reports/manuscript/paper_changes.tex
Line ending thingee.

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{ We approach differences between individuals through a ``decoding'' lens:}
We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{} and connectometry \cite{}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.

>>>>

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance.
\added{ We approach differences between individuals through a ``decoding'' lens:}
We predict the phenotypical variance in a group of subjects (or classify group membership), based on a linear combination of the features estimated with \replaced{tract profiling}{tractometry}
\added{This is unlike many previous models of white matter differences (e.g., TBSS \cite{smith2006tract} and connectometry \cite{yeh2016connectometry}) that are ``encoding'' models, where differences between individuals and groups are tested as hypotheses about differences in their brain features (i.e., in their tract profiles; the distinction between ``encoding'' and ``decoding'' and the terms stem from functional MRI literature \cite{Naselaris2011-ss})}.
